### 2013-07-29 Tex/chapters/results.tex
Evolution des RNG kurz erläutert

        \caption[Anomaly of the GG for Small $\sigma$]
        {
            GG with periodic boundary conditions for different \(\sigma = 0\)
        }
        \label{fig:GG_sigma}
    \end{figure}\\
    The explanation for the plateau of the RNG at low \(\sigma\) is similar.
    On the RNG no new edges arise at small displacements of the nodes\footnote{See appendix \ref{appendix:RNGDisplacement} for a graphic.}\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.}.
    But the degree does not alone influence the behavior of \(T_c\).
    Further \(T_c\) depends on the coupling constant \(J\), which is
    obvious in eq. \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
    coupling constant in turn is depending on the length of the edges,
    which changes with \(\sigma\).
    Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted. This is a number which should combine the dependence on
    the degree and the coupling constant. It is determined by summing
    over the edge weights of all edges connected to a node and averaging
    this value over all nodes. Alternatively it is the average edge weight
    of all edges multiplied by the degree.
    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:sumJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
        }
        \subfigure[][]
        {
            \label{sfig:sumJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
        }

>>>>

        \caption[Anomaly of the GG for Small $\sigma$]
        {
            GG with periodic boundary conditions for different \(\sigma = 0\)
        }
        \label{fig:GG_sigma}
    \end{figure}\\
    The evolution of the RNG with increasing \(\sigma\) can be made plausible
    with the same arguments. Fig. \ref{fig:RNG_sigma}
    shows, that for \(\sigma \lesssim 0.1\) the square lattice character is
    preserved -- no new edges arise neither many existing edges vanish, which
    explains the plateau in the \(T_{c}\) diagram. With
    increasing \(\sigma\), more and more edges vanish\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.},
    thus reducing the degree and \(T_{c}\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][$\sigma = 0.09$]
        {
            \label{sfig:RNG_sigma:0.09}
            \includegraphics[width=0.30\textwidth]{images/RNG/out009}
        }
        \subfigure[][$\sigma = 0.15$]
        {
            \label{sfig:RNG_sigma:0.15}
            \includegraphics[width=0.30\textwidth]{images/RNG/out015}
        }
        \subfigure[][$\sigma = 0.21$]
        {
            \label{sfig:RNG_sigma:0.21}
            \includegraphics[width=0.30\textwidth]{images/RNG/out021}
        }

        \caption[Anomaly of the RNG for Small $\sigma$]
        {
            RNG with periodic boundary conditions for different \(\sigma = 0\)
        }
        \label{fig:RNG_sigma}
    \end{figure}\\
    But the degree does not alone influence the behavior of \(T_c\).
    Further \(T_c\) depends on the coupling constant \(J\), which is
    obvious in eq. \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
    coupling constant in turn is depending on the length of the edges,
    which changes with \(\sigma\).
    Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted. This is a number which should combine the dependence on
    the degree and the coupling constant. It is determined by summing
    over the edge weights of all edges connected to a node and averaging
    this value over all nodes. Alternatively it is the average edge weight
    of all edges multiplied by the degree.
    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:sumJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
        }
        \subfigure[][]
        {
            \label{sfig:sumJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
        }
